\vspace{-1cm} \bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-04-06 latex/paper.tex
Remove biblatex usage
Final edits from Brill's suggestions

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
% \usepackage[charter]{mathdesign} % I hate how charter greeks look
%\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{microtype}
\graphicspath{{../figures/}}
\usepackage[style=authoryear-icomp,maxbibnames=9,maxcitenames=2,backend=biber]{biblatex}
%\bibliographystyle{unsrtapalike}
%\bibliography{bibttc.bib}
\addbibresource{\jobname.bib}
% title font size
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries\itshape}

@@

\textbf{Keywords}: Phosphatidylinositol 4,5-bisphosphate, Skittles, Cep290, cilia, transition zone

@@

\vspace{-0.5cm}
\begin{doublespacing}
  \begin{linenumbers}
    \section*{Abstract}
    Cilia are sensory organelles that are essential for human development
    and physiology.
    A large number of genetic disorders linked to cilium dysfunction are
    associated with proteins that localize to the ciliary transition zone (TZ),
    a structure at the base of cilia that regulates trafficking in and out
    of the cilium.
    Despite substantial effort to identify TZ proteins and their roles
    in cilium assembly and function,
    processes underlying maturation of TZs are not well understood.
    Here, we report a role for the membrane lipid
    phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) in TZ maturation
    in the \textit{Drosophila melanogaster} male germline.
    We show that reduction of cellular \PIP{} levels
    by ectopic expression of a phosphoinositide phosphatase
    or mutation of
    the type I phosphatidylinositol phosphate kinase Skittles
    induces formation of longer than normal TZs.
    These hyperelongated TZs exhibit functional defects,
    including loss of plasma membrane tethering.
    We also report that the \textit{onion rings} (\textit{onr}) allele
    of Drosophila Exo84
    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
    by promoting proper TZ maturation.
    \newpage

@@

    Ciliogenesis begins with assembly of a nascent TZ at the tip of
    the basal body (BB) \citep{reiter2012base}.
    During TZ maturation, its structure and protein
    composition change, allowing for
    establishment of a compartmentalized space, bounded by the ciliary membrane
    and the TZ, where assembly of the axoneme, a microtubule-based structure
    that forms the core of cilia,
    and signalling can occur.
    In Drosophila, nascent TZs first assemble on BBs
    during early G2 phase in primary spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with anchoring of cilia to the plasma membrane (PM),
    microtubule remodelling within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    Paramecium \citep{aubusson2015transition},
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    Drosophila \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

    We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) is essential for formation of the axoneme in the Drosophila
    male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    \PIP{}, one of seven different phosphoinositides (PIPs) present in eukaryotes,
    localizes primarily to the PM, where it is required for
    vesicle trafficking, among
    other processes \citep{balla2013phosphoinositides}.
    \PIP{} has recently been linked to cilium function.
    Although the ciliary membrane contains very little \PIP{} due to the action
    of the cilium resident PIP phosphatase INPP5E,
    the base of the cilium is enriched in \PIP{}
    \citep{nakatsu2015phosphoinositide}.
    Inactivation of INPP5E causes a build up of intraciliary \PIP{},
    which disrupts transport of Hedgehog signalling proteins in vertebrates
    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}
    and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
    In light of the current understanding of the role
    for \PIP{} as a modulator of cilium function,
    we sought to investigate the cause of defects we had observed
    in axoneme assembly in Drosophila male germ cells
    with reduced levels of \PIP{} \citep{wei2008depletion, fabian2010phosphatidylinositol}.

    \section*{Results}
    % 
    % Results - 1
    % 
    \subsection*{\PIP{} is essential for transition zone maturation}
    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella PIP phosphatase SigD
    under control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
    (hereafter \sigd{})
    \citep{wei2008depletion}.
    To examine whether axoneme defects in \sigd{}
    \citep{wei2008depletion}
    were caused by aberrant TZ function,
    we examined localization of fluorescently-tagged
    centriolar/BB protein
    Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
    and conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly.
    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase,
    when TZs are still immature.
    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
    compared to controls by late G2 phase, following
    the period of TZ maturation (Figure 1B and 1C).
    Unlike Drosophila \textit{cep290} mutants, which contain
    longer than normal BBs \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1D).
    Consistent with this result, the ultrastructure of BBs in \sigd{}
    is normal, and localization of the centriolar
    marker GFP-PACT \citep{basto2006flies}
    is similar in controls and \sigd{} \citep{wei2008depletion}.
    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition, pratt2016drosophila}
    exhibited hyperelongation in \sigd{} (Figure 1E),
    indicating that this phenotype is not unique to Cep290.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%)
    and showed high correlation (\textgreater 0.95)
    within syncytial germ cell cysts,
    suggestive of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite persistence of hyperelongated TZs through meiosis,
    axonemes were able to
    elongate normally in post-meiotic cells (Figure 1F).
    Nonetheless, the ultrastructure of these axonemes
    is frequently aberrant,
    either lacking nine-fold symmetry or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    % 
    % Results - 2
    % 
    \subsection*{The type I PIP kinase (PIPKI) Skittles (Sktl) regulates TZ length}
    Although \PIP{} is its major substrate in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can dephosphorylate multiple PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype due to decreased \PIP{},
    we attempted to rescue it by
    co-expressing \sigd{} with
    fluorescently-tagged Skittles (Sktl)
    under control of $\beta$\textsubscript{2}-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and 2B).
    Furthermore, the BB/TZ protein Unc-GFP
    \citep{baker2004mechanosensory, wei2008depletion},
    exhibited TZ hyperelongation at a low penetrance in \textit{sktl}$^{2.3}$
    mutant clones (Figure 2C),
    indicating that Sktl is important for TZ maturation.

    Vertebrate PIPKI$\gamma$ is important for cilium formation in cultured cells
    \citep{xu2016phosphatidylinositol}.
    The two Drosophila PIPKIs, Sktl and PIP5K59B,
    arose from recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
    Sktl has diverged more than its paralog PIP5K59B, and seems
    to be functionally related to PIPKI$\gamma$
    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
    by promoting CP110 removal from BBs \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length but not TZ assembly. 
    Notably, neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    is removed from BBs in early primary spermatocytes
    \citep{franz2013cp110}.

    % 
    % Results - 3
    % 
    \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
    We next sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    Following meiosis in the Drosophila male germline, TZs detach from
    the BB and migrate along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    As shown by Unc and Cep290 localization,
    TZs in \sigd{} were frequently incapable of detaching from
    BBs and migrating along axonemes despite
    axoneme elongation (Figure 1E) and cell elongation
    (Figures 3A and 3B).
    The previously reported ``comet-shaped'' Unc-GFP localization in \sigd{}
    \citep{wei2008depletion}
    persists during cell elongation after meiosis
    (Figure 3A, bottommost panel)
    despite elongation of the axoneme (Figure 1E).

    In Drosophila and humans, BBs consist of microtubule triplets
    \citep{jana2016drosophila, lattao2017centrioles},
    whereas axonemes contain microtubule doublets due to obstruction of
    C-tubules at the TZ \citep{gottardo2013cilium}.
    Consistent with a defect in this barrier and the presence of
    microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
    a subset of cilia (<5\%) in \sigd{}
    contained puncta of the core centriolar protein Ana1 at the distal
    tips of TZs (Figure 3C).
    Treatment of germ cells with the microtubule-stabilizing drug
    Taxol increased the penetrance of this phenotype from <5\% in untreated cells
    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (arrowheads in Figure 3D)
    without significantly affecting Cep290 length (Figure 3E).
    Taxol-treated controls did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
    Fluorescently-tagged pericentriolar protein Asterless (CEP152 homolog)
    \citep{blachon2008drosophila, dzhindzhev2010asterless},
    did not localize to TZ-distal puncta in \sigd{} ($p$ <0.01)
    suggesting that these TZ-distal
    sites are not fully centriolar in protein composition.
    Taxol has been hypothesized to disrupt TZ maturation
    by inhibiting microtubule remodelling in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
    Similar to \sigd{},
    Taxol-treated male germ cells assemble extremely long axonemes
    that contain triplet microtubules
    \citep{riparbelli2013unique}, further supporting a functional relationship between
    \PIP{} and microtubule reorganization in TZ maturation.

@@

    Due to involvement of the exocyst in trafficking at the PM,
    we examined whether cilium-associated membranes were affected in \sigd{}
    or \textit{onr} mutants in a manner similar to \textit{dilatory; cby} mutants
    \citep{vieillard2016transition}. 
    Dilatory (Dila), a conserved TZ protein, cooperates with Cby to assemble TZs in
    the Drosophila male germline \citep{vieillard2016transition}.
    Whereas TZs in \sigd{} and \textit{onr} cells were able to dock
    at the PM initially, they were unable to maintain
    membrane connections, and were rendered cytoplasmic (Figure 4B and C) similar to TZs in
    \textit{dila; cby} mutants.
    We found that fluorescently-tagged Exo70, a \PIP{}-binding exocyst subunit,
    localized to BBs (Figure 4D).
    Our results suggest that the exocyst, and Exo84 in particular, regulates
    cilium-membrane associations, similar to \PIP{}, and that TZ hyperelongation and loss of
    membrane-cilium association are genetically separable phenotypes.

    \section*{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional one,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base, gonccalves2017ciliary}.
    In the Drosophila male germline, TZ maturation occurs during the
    extended G2 phase in mature primary spermatocytes prior to meiosis, and can be readily
    observed by an increase in TZ length using fluorescence microscopy.
    Our results suggest that normal execution of this process
    requires \PIP{} and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Similar to \sigd{}, Drosophila \textit{dila; cby} and \textit{cby}
    mutants display hyperelongated TZs
    \citep{enjolras2012drosophila,vieillard2016transition},
    whereas \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila}.
    Because both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} seems to regulate TZ length independently of an effect on Cby or Mks1 recruitment.

    We also show that hyperelongated TZs are dysfunctional.
    Similar to \textit{dila}; \textit{cby} \citep{vieillard2016transition} and
    \textit{cep290} \citep{basiri2014migrating}
    mutants, axonemes can assemble in \sigd{}, albeit
    with aberrant ultrastructure
    \citep{wei2008depletion}, despite the lack of functional TZs
    or membrane association.
    The presence of TZ-distal Ana1 puncta in \sigd{} cells, without an increase
    in BB length seen in \textit{cep290} mutants lacking a functional TZ barrier,
    suggests that \sigd{} expression selectively disrupts the ability of TZs to restrict C-tubules and
    Ana1 without abolishing the TZ barrier entirely.
    CEP295, the human Ana1 ortholog, regulates
    post-translational modification of centriolar
    microtubules \citep{chang2016cep295}, which may explain the presence of Ana1 along with
    supernumerary microtubules in \sigd{} cells.
    Asterless (Asl), a pericentriolar protein
    important for centrosome formation and centriole duplication
    \citep{blachon2008drosophila, dzhindzhev2010asterless}, did not
    exhibit this TZ-distal localization, possibly due to different dynamics of Ana1 and Asl
    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} and the
    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.

@@

    \section*{Methods}
    \subsection*{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion}.
    GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
    and transgenic flies were generated using standard \textit{P} element-mediated transformation.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    Clones were induced by heat shock for two hours on days 3, 4 and 5 after egg laying.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

    \subsection*{Antibodies}
    The following primary antibodies were used for immunofluorescence
    at the indicated concentrations ---
    chicken anti-GFP IgY (abcam), 1:1000;
    rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
    rabbit anti-Centrin (C7736, Sigma-Aldrich), 1:500;
    mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
    Secondary antibodies were Alexa 488- and Alexa 568-conjugated
    anti-mouse, anti-rabbit and anti-chicken
    IgG (Molecular Probes) at 1:1000.
    DAPI at 1:1000 was used to stain for DNA.

@@

    \section*{Acknowledgements}
    We are grateful to Brian Ciruna for insightful discussions,
    B{\'e}n{\'e}dicte Durand for providing (at the time of experiments)
    unpublished fly stocks, and to
    B{\'e}n{\'e}dicte Durand and Bill Trimble
    for comments on the manuscript.
    This research was supported by a grant from the Canadian Institutes for
    Health and Research to J.A.B (MOP \#130437).
    A.G. was supported by a
    University of Toronto Open Fellowship and
    an Ontario Graduate Scholarship.

@@

    \item TZ hyperelongation persists through meiosis but does not affect

@@

      Images were chosen to demonstrate the variety in Cep290 distribution.

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
%\usepackage[charter]{mathdesign} % I hate how charter greeks look
\usepackage[numbers]{natbib}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{microtype}
\graphicspath{{../figures/}}
\bibliographystyle{unsrtapalike}

% title font size
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries\itshape}

@@

\textbf{Keywords}: PtdIns(4,5)P\textsubscript{2}, Skittles, Cep290, cilia, transition zone, basal body

@@

\vspace{-0.5cm}
\begin{doublespacing}
  \begin{linenumbers}
    \section*{Abstract}
    Cilia are cellular antennae that are essential for human development
    and physiology.
    A large number of genetic disorders linked to cilium dysfunction are
    associated with proteins that localize to the ciliary transition zone (TZ),
    a structure at the base of cilia that regulates trafficking in and out
    of the cilium.
    Despite substantial effort to identify TZ proteins and their roles
    in cilium assembly and function,
    processes underlying maturation of TZs are not well understood.
    Here, we report a role for the membrane lipid
    phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) in TZ maturation
    in the \textit{Drosophila melanogaster} male germline.
    We show that reduction of cellular \PIP{} levels
    by ectopic expression of a phosphoinositide phosphatase
    or mutation of
    the type I phosphatidylinositol phosphate kinase Skittles
    induces formation of longer than normal TZs.
    These hyperelongated TZs exhibit functional defects,
    including loss of plasma membrane tethering.
    We also report that the \textit{onion rings} (\textit{onr}) allele
    of Drosophila \textit{exo84}
    decouples TZ hyperelongation from loss of cilium-plasma membrane tethering.
    Our results reveal a requirement for \PIP{} in supporting ciliogenesis
    by promoting proper TZ maturation.
    \newpage

@@

    Ciliogenesis begins with assembly of a nascent TZ at the tip of
    the basal body (BB) \citep{reiter2012base}.
    During TZ maturation, its structure and protein
    constituents change, allowing for
    establishment of a compartmentalized space, bounded by the ciliary membrane
    and the TZ, where assembly of the axoneme, a microtubule-based structure
    that forms the ciliary core,
    and signalling can occur.
    In Drosophila, nascent TZs first assemble on BBs
    during early G2 phase in primary spermatocytes \citep{riparbelli2012assembly}.
    This occurs concomitantly with anchoring of cilia to the plasma membrane (PM),
    microtubule remodelling within the TZ \citep{gottardo2013cilium},
    and establishment of a
    ciliary membrane that will persist through meiosis
    \citep{riparbelli2012assembly} (Figure 1A).
    TZ maturation has been described in
    Paramecium \citep{aubusson2015transition},
    \textit{Caenorhabditis elegans} \citep{serwas2017centrioles} and
    Drosophila \citep{gottardo2013cilium},
    and is most readily observed by an increase in TZ length
    in the Drosophila male germline.

    We previously showed that the membrane lipid phosphatidylinositol 4,5-bisphosphate
    (\PIP{}) is essential for formation of the axoneme in the Drosophila
    male germline \citep{wei2008depletion, fabian2010phosphatidylinositol}.
    \PIP{}, which is one of seven different phosphoinositides (PIPs) present in eukaryotes,
    localizes primarily to the PM, where it is required for
    vesicle trafficking, among
    other processes \citep{balla2013phosphoinositides}.
    \PIP{} has recently been linked to cilium function.
    Although the ciliary membrane contains very little \PIP{} due to the action
    of the cilium resident PIP phosphatase INPP5E,
    the base of the cilium is enriched in \PIP{}
    \citep{nakatsu2015phosphoinositide}.
    Inactivation of INPP5E causes a build up of intraciliary \PIP{},
    which disrupts transport of Hedgehog signalling proteins in vertebrates
    \citep{chavez2015modulation, garcia2015phosphoinositides, conduit2017compartmentalized}
    and ion channels involved in mechanotransduction in Drosophila \citep{park2015ciliary}.
    In light of the current understanding of \PIP{} as a modulator of cilium function,
    we sought to investigate the cause of defects we had observed
    in axoneme assembly in Drosophila male germ cells
    with reduced levels of \PIP{} \citep{wei2008depletion, fabian2010phosphatidylinositol}.

    \section*{Results}
    % 
    % Results - 1
    % 
    \subsection*{\PIP{} is essential for transition zone maturation}
    To investigate how reduction of cellular \PIP{} affects ciliogenesis in the
    Drosophila male germline,
    we used transgenic flies expressing the Salmonella PIP phosphatase SigD
    under control of spermatocyte-specific $\beta$\textsubscript{2}-tubulin promoter
    (hereafter \sigd{})
    \citep{wei2008depletion}.
    To examine whether axoneme defects in \sigd{}
    \citep{wei2008depletion}
    were caused by aberrant TZ function,
    we examined localization of fluorescently-tagged versions of the
    core centriolar/BB protein
    Ana1 (CEP295 homolog) \citep{goshima2007genes, blachon2009proximal}
    and the conserved TZ protein Cep290 \citep{basiri2014migrating}
    during early steps of cilium assembly.
    Cep290 distribution appeared similar in control and \sigd{} in early G2 phase,
    when TZs are still immature.
    In contrast, Cep290-labelled TZs were significantly longer in \sigd{}
    compared to controls by late G2 phase, following
    the period of TZ maturation (Figure 1B and 1C).
    Unlike Drosophila \textit{cep290} mutants, which contain
    longer than normal BBs \citep{basiri2014migrating},
    Ana1 length was not affected in \sigd{},
    and we did not observe a strong
    correlation between Cep290 and Ana1 lengths (Figure 1D).
    Consistent with this result, the ultrastructure of BBs in \sigd{}
    is normal, and localization of the centriolar
    marker GFP-PACT \citep{basto2006flies}
    is similar, in controls and \sigd{} \citep{wei2008depletion}.
    In contrast, TZ proteins Chibby (Cby) \citep{enjolras2012drosophila} and
    Mks1 \citep{vieillard2016transition, pratt2016drosophila}
    exhibited hyperelongation in \sigd{} (Figure 1E),
    indicating that this phenotype is not unique to Cep290.
    TZ hyperelongation was a highly penetrant phenotype (\textgreater 70\%)
    and showed high correlation (\textgreater 0.95)
    within syncytial germ cell cysts,
    suggestive of a dosage-based response to a shared cellular factor,
    presumably SigD.
    Despite persistence of hyperelongated TZs through meiosis,
    axonemes were able to
    elongate normally in post-meiotic cells (Figure 1F).
    Nonetheless, the ultrastructure of these axonemes
    is frequently aberrant,
    either lacking nine-fold symmetry or containing triplet microtubules
    in addition to the usual doublets \citep{wei2008depletion}.

    % 
    % Results - 2
    % 
    \subsection*{The type I PIP kinase Skittles regulates TZ length}
    Although \PIP{} is its major substrate in eukaryotic cells \textit{in vivo}
    \citep{terebiznik2002elimination, zhou2001salmonella, sengupta2013depletion},
    SigD can dephosphorylate multiple PIPs \textit{in vitro}
    \citep{norris1998sopb}.
    To address whether TZ hyperelongation observed in \sigd{} represented a
    physiologically relevant phenotype due to decreased \PIP{},
    we attempted to rescue this phenotype by
    co-expressing \sigd{} with
    fluorescently-tagged Skittles (Sktl)
    under control of $\beta$\textsubscript{2}-tubulin promoter.
    We found that Sktl expression was able to suppress TZ hyperelongation
    in a cilium-autonomous manner (Figure 2A and 2B).
    Furthermore, the BB/TZ protein Unc-GFP
    \citep{baker2004mechanosensory, wei2008depletion},
    exhibited TZ hyperelongation at a low penetrance in \textit{sktl}$^{2.3}$
    mutant clones (Figure 2C),
    indicating that Sktl is important for TZ maturation.

    Vertebrate type I PIP kinase PIPKI$\gamma$ is important for cilium formation in cultured cells
    \citep{xu2016phosphatidylinositol}.
    The two Drosophila PIPKIs, Sktl and PIP5K59B,
    arose from recent duplication of
    the ancestral PIPKI gene,
    and are not orthologous to specific vertebrate PIPKI isoforms (Figure 2D).
    Sktl has diverged more than its paralog PIP5K59B and seems
    to be functionally related to PIPKI$\gamma$
    and the \textit{C. elegans} PPK-1 in having roles at cilia \citep{xu2014pipkigamma}.
    However, unlike the human PIPKI$\gamma$, which licenses TZ assembly
    by promoting CP110 removal from BBs \citep{xu2016phosphatidylinositol},
    our results suggest that Sktl functions in
    regulating TZ length but not TZ assembly. 
    Notably, neither inactivation nor overexpression of \textit{cp110} affects
    cilium formation in Drosophila, and Cp110
    is removed from BBs in early primary spermatocytes
    \citep{franz2013cp110}.

    % 
    % Results - 3
    % 
    \subsection*{Hyperelongated transition zones exhibit signs of functional defects}
    We next sought to examine whether TZ hyperelongation due to SigD expression
    affected TZ function.
    Following meiosis in the Drosophila male germline, TZs detach from
    the BB and migrate along the growing axoneme, maintaining a ciliary compartment
    at the distal-most {\raise.17ex\hbox{$\scriptstyle\sim$}}5$\mu$m where tubulin
    is incorporated into the axoneme
    \citep{basiri2014migrating, fabian2012drosophila}.
    As shown by Unc and Cep290 localization,
    TZs in \sigd{} were frequently incapable of detaching from
    BBs and migrating along axonemes despite
    axoneme and cell elongation
    (Figures 1E, 3A and 3B).
    Indeed, the previously reported ``comet-shaped'' Unc-GFP localization in \sigd{}
    \citep{wei2008depletion}
    persists during cell elongation after meiosis
    (Figure 3A, bottommost panel)
    despite elongation of the axoneme (Figure 1E).

    In Drosophila and humans, BBs consist of microtubule triplets
    \citep{jana2016drosophila, lattao2017centrioles},
    whereas axonemes contain microtubule doublets due to obstruction of
    C-tubules at the TZ \citep{gottardo2013cilium}.
    Consistent with a defect in this barrier and the presence of
    microtubule triplets in axonemes in \sigd{} \citep{wei2008depletion},
    a subset of cilia (<5\%) in \sigd{}
    contained puncta of Ana1 at the distal
    tips of TZs (Figure 3C).
    Treatment of germ cells with the microtubule-stabilizing drug
    Taxol increased the penetrance of this phenotype from <5\% in untreated cells
    to \textgreater25\% in cells treated with 4 $\mu$M Taxol (arrowheads in Figure 3D)
    without significantly affecting Cep290 length (Figure 3E).
    Taxol-treated controls did not exhibit TZ-distal Ana1 puncta ($p$ <0.01 at 5\% penetrance).
    Fluorescently-tagged Asterless (CEP152 homolog), a pericentriolar protein
    \citep{blachon2008drosophila, dzhindzhev2010asterless},
    did not localize to TZ-distal puncta in \sigd{} ($p$ <0.01)
    suggesting that these TZ-distal
    sites are not fully centriolar in protein composition.
    Taxol has been hypothesized to disrupt TZ maturation
    by inhibiting microtubule remodelling in the Drosophila male germline \citep{riparbelli2012assembly, riparbelli2013unique}.
    Similar to \sigd{},
    Taxol-treated male germ cells assemble extremely long axonemes
    that contain triplet microtubules
    \citep{riparbelli2013unique}, further supporting a functional relationship between
    \PIP{} and microtubule reorganization in TZ maturation.

@@

    Due to involvement of the exocyst in trafficking at the PM,
    we examined whether cilium-associated membranes were affected in \sigd{}
    or \textit{onr} mutants in a manner similar to \textit{dilatory; cby} mutants
    \citep{vieillard2016transition}. 
    Dilatory (Dila), a conserved TZ protein, cooperates with Cby to assemble TZs in
    the Drosophila male germline \citep{vieillard2016transition}.
    Whereas TZs in \sigd{} and \textit{onr} cells were able to dock
    at the PM initially, they were unable to maintain
    membrane connections, and were rendered cytoplasmic (Figure 4B and C), similar to TZs in
    \textit{dila; cby} mutants.
    We found that fluorescently-tagged Exo70, a \PIP{}-binding exocyst subunit,
    localized to BBs (Figure 4D).
    Our results suggest that the exocyst, and Exo84 in particular, regulates
    cilium-PM associations, similar to \PIP{}, and that TZ hyperelongation and loss of
    cilium-PM association are genetically separable phenotypes.

    \section*{Discussion}
    The process of maturation of a TZ from a nascent form to a fully functional state,
    leading ultimately to axoneme assembly and ciliary signalling,
    requires orchestration of various proteins and cellular pathways
    \citep{reiter2012base, gonccalves2017ciliary}.
    Our results indicate that normal execution of this process
    requires \PIP{} and that depletion of \PIP{} induces TZs to
    grow longer than normal.
    Similar to \sigd{}, Drosophila \textit{dila; cby} and \textit{cby}
    mutants display hyperelongated TZs
    \citep{enjolras2012drosophila,vieillard2016transition},
    whereas \textit{mks1} mutants have shorter TZs \citep{pratt2016drosophila}.
    Because both Cby and Mks1 are hyperelongated in \sigd{} cells,
    \PIP{} regulates TZ length independently of an effect on Cby or Mks1 recruitment.

    We also show that hyperelongated TZs are dysfunctional.
    Similar to \textit{dila}; \textit{cby} \citep{vieillard2016transition} and
    \textit{cep290} \citep{basiri2014migrating}
    mutants, axonemes can assemble in \sigd{}, albeit
    with aberrant ultrastructure
    \citep{wei2008depletion}, despite the lack of functional TZs
    or membrane association.
    The presence of TZ-distal Ana1 puncta in \sigd{} cells, without the increase
    in BB length seen in \textit{cep290} mutants lacking a functional TZ barrier,
    suggests that \sigd{} expression selectively disrupts the ability of TZs to restrict C-tubules and
    Ana1 without abolishing the TZ barrier entirely.
    CEP295, the human Ana1 ortholog, regulates
    post-translational modification of centriolar
    microtubules \citep{chang2016cep295}, which may explain the presence of Ana1 along with
    supernumerary microtubules in \sigd{} cells.
    Asterless (Asl), a pericentriolar protein
    important for centrosome formation and centriole duplication
    \citep{blachon2008drosophila, dzhindzhev2010asterless}, did not
    exhibit this TZ-distal localization, possibly due to differences dynamics of Ana1 and Asl
    loading onto centrioles \citep{fu2016conserved, saurya2016drosophila} or the
    more peripheral nature of Asl within the centriole \citep{blachon2008drosophila}.

@@

    \section*{Methods}
    \subsection*{Transgenic flies}
    Drosophila stocks were cultured on cornmeal molasses agar medium at 25$^{\circ}$C
    and 50\% humidity.
    Stocks expressing $\beta$\textsubscript{2}t::\textit{Styp}\textbackslash{SigD} (chromosome \textit{3}) and
    $\beta$\textsubscript{2}t::YFP-Sktl (chromosome \textit{2}) were described previously \citep{wei2008depletion, wong2005pip2}.
    GFP-Exo70 was cloned into the low-level expression vector \textit{tv3} \citep{wong2005pip2}
    and transgenic flies were generated using standard \textit{P} element-mediated transformation.
    Ana1-tdTomato (chromosome \textit{2}) and Cep290-GFP (chromosome \textit{3}) were provided
    by T. Avidor-Reiss \citep{basiri2014migrating}.
    \textit{Sp}/\textit{CyO}; Unc-GFP was originally provided by M. Kernan \citep{baker2004mechanosensory}.
    Stocks expressing GFP-tagged Chibby and Mks1 were
    provided by B. Durand \citep{enjolras2012drosophila, vieillard2016transition}.
    The \textit{onr} mutant was described previously \citep{giansanti2015exocyst}.
    Stocks for generating \textit{sktl}\textsuperscript{2.3} clones were originally provided by
    A. Guichet \citep{gervais2008pip5k}.
    Clones were induced by heat shock for two hours on days 3, 4 and 5 after egg laying.
    \textit{w}\textsuperscript{1118} was used as the wild-type control.

    \subsection*{Antibodies}
    The following primary antibodies were used for immunofluorescence
    at the indicated concentrations: 
    chicken anti-GFP IgY (abcam), 1:1000;
    rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
    rabbit anti-Centrin (C7736, Sigma-Aldrich), 1:500;
    mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
    Secondary antibodies were Alexa 488- and Alexa 568-conjugated
    anti-mouse, anti-rabbit and anti-chicken
    IgG (Molecular Probes) at 1:1000.
    DAPI at 1:1000 was used to stain for DNA.

@@

    \section*{Acknowledgements}
    We are grateful to Brian Ciruna for insightful discussions,
    B{\'e}n{\'e}dicte Durand, Tomer Avidor-Reiss, Antoine Guichet and Maurice Kernan for providing
    unpublished fly stocks, and to
    B{\'e}n{\'e}dicte Durand and Bill Trimble
    for comments on the manuscript.
    This research was supported by a grant from the Canadian Institutes for
    Health and Research to J.A.B (MOP \#130437).
    A.G. was supported by a
    University of Toronto Open Fellowship and
    an Ontario Graduate Scholarship.

@@

    \item TZ hyperelongation persists through meiosis (white arrowhead) but does not affect

@@

      Images demonstrate the variety in Cep290 distribution.
      Yellow arrowheads mark TZ-distal Ana1.
